Ontario Graduate Scholarship: Plan of Study

### 2020-04-13 latex/ogs/main.tex
Update to final v3

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
smoothly swing their legs based on their current speed and position
\cite{pendulum_length_giant_gymnastics}. In doing so, they are able to generate
enough momentum to perform backflips on the bar. When controlling mechanical
systems, standard practice is to have a robot's actuators track a function of
time. Much like the gymnast, this can produce unnatural motion.  The recent
techniques of virtual constraints offer the ability to track a function of speed
and position to produce realistic, biologically plausible motion.

>>>>

When a gymnast is performing a swing-up routine on a bar, they do not kick their
feet at specified time intervals. Rather, a more natural human motion is to
smoothly swing their legs based on their current speed and position
\cite{pendulum_length_giant_gymnastics}. In doing so, they are able to generate
enough momentum to perform backflips on the bar. When controlling mechanical
systems, standard practice is to have a robot's actuators track a function of
time. Much like the gymnast, it can be more natural to have the robot track a
function of speed and position instead. The recent techniques of virtual
constraints offer this ability to produce realistic, biologically plausible
motion.
